---
title: "dataWrangling"
author: "Madelyn Hair"
date: "2023-01-28"
output: html_document
---
### For use when updating raw data only 
IGNORE this chunk unless raw data was updated from BORIS
```{r}
#all <- read_csv("data/allevents.csv")
#all[c("ind", "obs")] <- str_split_fixed(all$`Observation id`, " ", 2)
#all$date <- as.Date(all$`Observation date`)
#all$time <- format(as.POSIXct(all$`Observation date`), format = "%H:%M:%S")

#write.csv(all, "data/all.csv")
```

Then go into excel and find/replace "|" for "AND" : Should be 51 replacements 

Also, create a new table called rtime and make it = Start (s) / 86400 + time




## Start Here

Packages
```{r}
library(tidyverse)
library(gdata)
library(magrittr)
library(hms)
```



Read data and assign subject taxa
```{r}
all1 <- read.csv("data/all.csv")
all1[c('m1', 'm2')] <- str_split_fixed(all1$Modifiers, "AND",2)  
all1 <- all1 %>%
  mutate(Subject_tax  = dplyr::case_when(Subject %in% c("Clam1", "Clam2", "Clam3")~ "Clam", Subject %in% c("Hermit Crab1", "Hermit Crab2", "Hermit Crab3") ~ "Hermit Crab", Subject%in%c("Swim Crab1", "Swim Crab2", "Swim Crab3") ~ "Swim Crab", Subject%in%c("Snail1", "Snail2", "Snail3") ~ "Snail", Subject == "Octopus" ~ "Octopus", TRUE ~ "error"))
all1$rtime <- as_hms(all1$rtime)


```

Assign accurate exposure levels
```{r}

l2 <- all1 %>% 
  filter(ind == "Loki", Experimental.Day %in% c(1,2)) %>%
  mutate(exposure = "pre") %>%
  mutate(bottle = "NA")
lexp <- all1 %>%
  filter(ind == "Loki", Experimental.Day == 6)  %>%
  mutate(exposure = case_when(rtime >= 45600 ~ 'active',rtime < 45600 ~ 'pre',  TRUE ~ 'error')) %>%
  mutate(bottle = case_when(rtime >= 45600 ~ 'post', rtime < 45600 ~ 'pre', TRUE ~ 'error'))
lpost<- all1%>%
  filter(ind == "Loki", Experimental.Day==9) %>%
  mutate(exposure = "post") %>%
  mutate(bottle = case_when(rtime < 38100 ~ 'pre', rtime >= 38100 ~ 'post'))
rpre1 <- all1%>%
  filter(ind == "Ragnar", Experimental.Day == 1) %>%
  mutate(exposure = "pre") %>%
  mutate(bottle = case_when(rtime < 37920 ~ 'pre', rtime >= 37920 ~ 'post'))
rpre2 <- all1%>%
  filter(ind == "Ragnar", Experimental.Day==2) %>%
  mutate(exposure = "pre") %>%
  mutate(bottle = 'NA')
rexp <- all1 %>%
  filter(ind == "Ragnar", Experimental.Day == 6)  %>%
  mutate(exposure = case_when(rtime >= 45180 ~ 'active',rtime < 45180 ~ 'pre',  TRUE ~ 'error')) %>%
  mutate(bottle = case_when(rtime < 45180 ~ 'pre', rtime >= 45180 ~ 'post'))
rpost <- all1 %>%
   filter(ind == "Ragnar", Experimental.Day==9)  %>%
  mutate(exposure = 'post') %>%
  mutate(bottle= case_when(rtime < 38700 ~ 'pre', rtime >= 38700 ~ 'post'))

hpre <- all1 %>%
   filter(ind == "Haliai", Experimental.Day == 1)  %>%
  mutate(exposure = 'pre') %>%
  mutate(bottle = case_when(rtime < 39780 ~ 'pre', rtime >= 39780 ~ 'post'))
hpre2 <- all1 %>%
   filter(ind == "Haliai", Experimental.Day==2)  %>%
  mutate(exposure = 'pre') %>%
  mutate(bottle = 'NA')
hexp <- all1%>%
   filter(ind == "Haliai", Experimental.Day==6)  %>%
  mutate(exposure = case_when(rtime >= 44700 ~ 'active', rtime < 44700 ~ 'pre',  TRUE ~ 'error')) %>%
  mutate(bottle = case_when(rtime < 44700 ~ 'pre', rtime >= 44700 ~ 'post'))
hpost <- all1 %>%
   filter(ind == "Haliai", Experimental.Day==9)  %>%
  mutate(exposure = 'post') %>%
  mutate(bottle = case_when(rtime < 382200 ~ 'pre', rtime >= 38220 ~ 'post'))
caly1 <- all1%>%
  filter(ind== "Caly", Experimental.Day==1) %>%
  mutate(exposure = 'pre') %>%
  mutate(bottle = case_when(rtime < 45300 ~ 'pre', rtime >= 45300 ~ 'post'))
caly2 <- all1%>%
  filter(ind== "Caly", Experimental.Day==2) %>%
  mutate(exposure = 'pre') %>%
  mutate(bottle = case_when(rtime < 45120 ~ 'pre', rtime >= 45120 ~ 'post'))
caly6 <- all1%>%
  filter(ind== "Caly", Experimental.Day==6) %>%
  mutate(exposure = case_when(rtime < 44940 ~ 'pre', rtime >= 44940 ~ "active")) %>%
  mutate(bottle = case_when(rtime < 44940 ~ 'pre', rtime >= 44940 ~ 'post'))
caly9 <- all1%>%
  filter(ind== "Caly", Experimental.Day==9) %>%
  mutate(exposure = 'post') %>%
  mutate(bottle = case_when(rtime < 45240 ~ 'pre', rtime >= 45240 ~ 'post'))
scyl1<- all1%>%
  filter(ind== "Scylla", Experimental.Day==1) %>%
  mutate(exposure = 'pre') %>%
  mutate(bottle = case_when(rtime < 44880 ~ 'pre', rtime >= 44880 ~ 'post'))
scyl2 <-all1%>%
  filter(ind== "Scylla", Experimental.Day==2) %>%
  mutate(exposure = 'pre') %>%
  mutate(bottle = case_when(rtime < 45060 ~ 'pre', rtime >= 45060 ~ 'post'))
scyl6 <-all1%>%
  filter(ind== "Scylla", Experimental.Day==6) %>%
  mutate(exposure = case_when(rtime < 44940 ~ 'pre', rtime >= 44940 ~ 'active')) %>%
  mutate(bottle = case_when(rtime < 44940 ~ 'pre', rtime >= 44940 ~ 'post'))
scyl9 <- all1%>%
  filter(ind== "Scylla", Experimental.Day==9) %>%
  mutate(exposure = 'post') %>%
  mutate(bottle = case_when(rtime < 45060 ~ 'pre', rtime >= 45060 ~ 'post'))
selk1 <- all1%>%
  filter(ind== "Selkie", Experimental.Day==1) %>%
  mutate(exposure = 'pre') %>%
  mutate(bottle = case_when(rtime < 44940 ~ 'pre', rtime >= 44940 ~ 'post'))
selk2 <- all1%>%
  filter(ind== "Selkie", Experimental.Day==2) %>%
  mutate(exposure = 'pre') %>%
  mutate(bottle = case_when(rtime < 45000 ~ 'pre', rtime >= 45000 ~ 'post'))
selk6 <- all1%>%
  filter(ind== "Selkie", Experimental.Day==6) %>%
  mutate(exposure = case_when(rtime < 45000 ~ 'pre', rtime >= 45000 ~ 'active')) %>%
  mutate(bottle = case_when(rtime < 45000 ~ 'pre', rtime >= 45000 ~ 'post'))
selk9 <- all1%>%
  filter(ind== "Selkie", Experimental.Day==9) %>%
  mutate(exposure = 'post') %>%
  mutate(bottle = case_when(rtime < 45180 ~ 'pre', rtime >= 45180 ~ 'post'))



all2 <- bind_rows(l2, lexp, lpost, rpre1, rpre2, rexp, rpost, hpre, hpre2, hexp, hpost, caly1, caly2, caly6, caly9, scyl1, scyl2, scyl6, scyl9, selk1, selk2, selk6,selk9)
dif <- anti_join(all1, all2) #Should be 0! 


sub <- all2 %>%
  filter(!date %in% c("7/15/22")) %>%
  mutate(rphoto = case_when(rtime <43200 ~ 'day', rtime <= 47520 ~ 'crep', TRUE ~ 'night'))
sub1 <- all2 %>%
  filter(date %in% c('7/15/22', '11/15/22')) %>%
  mutate(rphoto = case_when(rtime < 43200 ~ "day", rtime >= 43200 ~ 'crep', TRUE ~ 'error'))
all3<-bind_rows(sub,sub1)


```


Create Custom Behaviors, assign Activity Levels and Experimental Block. Export point (predation and color changes) data here
```{r}
all3 <- all3 %>%
  mutate(newbehav = case_when(Behavior == "Roaming" ~ "Roaming", Behavior == "Stationary" & m1 == "Alert Sitting" ~ 'Stationary- Active', Behavior == "Burrow" ~ "Stationary- Burrowed", Behavior == "left" ~ 'Left', Behavior == "right" ~ "Right", Behavior == "Under Refuge" ~ "Under Refuge", Behavior == "Unobservable" ~ "Unobservable", Subject_tax %in% c("Octopus", "Hermit Crab", "Swim Crab") & Behavior == "Stationary" & m1 == "Unknown" ~ "Stationary- Unknown", Behavior == "Climb" ~ "Climb",     ###General Behaviors
                              Subject_tax == "Octopus" & Behavior == "Stationary" & m1 %in% c("Quiet", "Active") ~ "Stationary- Sleeping", Subject_tax == "Octopus" & Behavior == "Feeding" ~ "Feeding", Subject_tax == "Octopus" & Behavior == "Predation" & m2 =="Successful" ~ "Predation Success", Subject_tax == "Octopus" & Behavior == "Predation" & m2 == "Failed" ~ "Predation Fail",Subject_tax == "Octopus" & Behavior == "Grope" ~ "Predation-Grope", Subject_tax == "Octopus" & Behavior == "Color change" ~ "Color Change",           ###Octopus behaviors 
  Subject_tax %in% c("Clam", "Snail") & Behavior == "Stationary" & m1 == "Unknown" ~ "Stationary- Inert")) %>%
  mutate(actlevel = case_when(newbehav == "Roaming" ~ 4, newbehav %in% c("Stationary- Active", "Feeding") ~ 3, newbehav %in% c("Stationary- Inert", "Stationary- Unknown") ~ 2, newbehav == "Stationary- Burrowed" ~ 1))

all3<-all3 %>%
  mutate(block = case_when(ind %in% c("Scylla", "Caly", "Selkie") ~ 2, TRUE ~ 1))
unique(all3$Behavior)

#Export data for predation events
write_csv(all3, "data/pred.csv")
```


### Wrangling for activity budget data
Fix Behaviors that span multiple experimental periods
```{r}
library(hms)
library(lubridate)
library(tidyverse)

all4 <- all3 %>%
  mutate(newstart = Start..s., newstop = Stop..s., newduration = Duration..s., row = row_number()) %>%mutate(date=as.Date(date,format="%m/%d/%Y")) %>%
  mutate(Experimental.Day = as.factor(Experimental.Day), 
         rtime = hms::as_hms(rtime)) %>%
  mutate(rownum = row_number())


#Extract the problematic rows that span the pre 12:30 and post 12:30 periods.
df <- all4 %>%
  mutate(stoptime = rtime + newduration) %>% 
  mutate(stoptime= as_hms(stoptime))%>%
  filter(rtime <= 45000 & stoptime >45000) 


#This will be the "pre" period on exposure day
df1 <-df %>%
  filter(Experimental.Day==6) %>%
  mutate(stoptime = as_hms('12:30:00')) %>%
  mutate(dur = stoptime-rtime) %>%
  mutate(exposure = "pre", bottle = "pre")  %>%
  mutate(dur = as.numeric(dur))
#Last step is necessary because some of the bottles were added at 12:28 or 29. 

#and this will be the 'post' period on exposure day
df2 <-df %>%
  filter(Experimental.Day==6)%>%
  mutate(rtime= as_hms('12:30:00'), dur = stoptime-45000) %>%
  mutate(exposure = "active", bottle = "post") %>%
  mutate(dur = as.numeric(dur))

#Now same thing for all other days
#Before 12:30
df3 <- df %>%
  filter(Experimental.Day !=6) %>%
  mutate(stoptime = as_hms('12:30:00')) %>%
  mutate(dur = stoptime-rtime) %>%
  mutate(dur = as.numeric(dur))

#After 12:30
df4 <-df %>%
  filter(!Experimental.Day==6)%>%
  mutate(rtime= as_hms('12:30:00'), dur = stoptime-45000) %>%
  mutate(dur = as.numeric(dur))


all5 <- all4 %>%
  mutate(stoptime = rtime + newduration) %>%
  mutate(stoptime = as_hms(stoptime)) %>%
  mutate(dur = as.numeric(newduration))


all6=all5%>%dplyr::slice(-as_vector(select(df,rownum)))%>%bind_rows(df1,df2, df3, df4)
```


Cut behaviors short at 14:00
```{r}
all7 <- all6 %>%mutate(row_id=row_number())
#Extract problematic rows that span 14:00
extra <- all7 %>%
  filter(stoptime >= 50400 & rtime <= 50400) 
fixed<-extra %>%
  mutate(stoptime = as_hms('14:00:00')) %>%
  mutate(dur = as.numeric(stoptime-rtime))

all8<- all7 %>%dplyr::slice(-as_vector(select(fixed,row_id))) %>%
  bind_rows(fixed)

```

Assign  exposure levels again
```{r}

#Undo the nuance and make it set to 12:30 for each 
all9 <- all8 %>%
  mutate(exposure = case_when(Experimental.Day %in% c(1,2) ~ 'pre', Experimental.Day == 6 & rtime < 45000 ~ 'pre', Experimental.Day == 6 & rtime >= 45000~'active', Experimental.Day == 9 ~ 'post', TRUE ~ 'error'))

sub <- all9 %>%
  filter(!date %in% c("7/15/22")) %>%
  mutate(rphoto = case_when(rtime <43200 ~ 'day', rtime <= 47520 ~ 'crep', TRUE ~ 'night'))
sub1 <- all9 %>%
  filter(date %in% c('7/15/22', '11/15/22')) %>%
  mutate(rphoto = case_when(rtime < 43200 ~ "day", rtime >= 43200 ~ 'crep', TRUE ~ 'error'))
allLOT<-bind_rows(sub,sub1)


```

This datasheet can only be used for state events (activity budgets) now
```{r}
#complete data set for activity budgets
write.csv(allLOT, "data/all1.csv")

sub <-allLOT %>%
  filter(rtime >= 45000 & rtime <= 50400)%>%
  filter(Experimental.Day != 1) %>%
  subset(select = -c(row, rownum, row_id, Behavioral.category, X, Description, Media.file, FPS, Human.Disturbance, time, Photoperiod
                     ))
#dataset truncated to experimental sampling period (12:30-14:00)
write.csv(sub, 'data/sub1.csv')

```


