---
title: "Left-Right"
author: "Madelyn Hair"
date: "2023-05-16"
output: html_document
---
```{r}
library(tidyverse)
library(hms)
```

Load R environment with complete models: Do this to skip running the bayesian bournoilli models
```{r}

load("Workspaces/Left-Right.RData")
```

**Create the thesis theme: these_thesi**
```{r}
theme_thesi <- function() {
  font <- 'Trebuchet MS' #Same as PPT
  theme_bw() %+replace%
    theme(
      
      #Gridlines
      panel.grid.major.x=element_blank(),
      panel.grid.major.y =element_blank(),
      panel.grid.minor.y=element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.border = element_blank(),
      axis.line = element_line(colour = "black"),
      plot.margin = margin(r= 5, t = 8, b = 8),
      
      #Text elements
      plot.title = element_text(family = font, 
                                size = 15, face = 'bold',
               hjust = -.15, vjust = 2),
      axis.title = element_text(family = font,
                                size = 12, face = 'bold'), 
      axis.title.y = element_text(margin= margin(r=5), angle = 90, size = 12),
      axis.title.x = element_blank(),
      axis.text = element_text(family = font,
                               size = 10),
      axis.text.x = element_text(margin = margin(t = 5), size = 10), 
      axis.text.y = element_text(face = 'bold', margin = margin(r = 5), size = 10),
      legend.text = element_text(size = 12),
      legend.title = element_text(size = 18),
      
      #facet labels
      strip.text.x = element_text(size = 15, face = 'bold', family =font),
      strip.background = element_blank()
    )
  
}

    
```
**Create the presentation theme_oct()!**
```{r}
theme_oct <- function() {
  font <- 'Trebuchet MS' #Same as PPT
  theme_bw() %+replace%
    theme(
      
      #Gridlines
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      panel.border = element_blank(),
      axis.line = element_line(colour = "black"),
       plot.margin = margin(r= 8, t = 8, b = 8, l = 8),
      #Text elements
      plot.title = element_text(family = font, 
                                size = 20,
                                face = 'bold',
                hjust = .5,
                                vjust = 2),
      axis.title = element_text(family = font,
                                size = 15, face = 'bold'), 
      #axis.title.x = element_blank(),
      axis.title.x = element_text(margin = margin(5)),
     # axis.title.y = element_text(margin= margin(r=10), angle = 90, size = 18),
     axis.title.y=element_blank(),
      axis.text = element_text(family = font,
                               size = 15),
     axis.text.y=element_text(margin=margin(r=5), face = "bold", size = 15),
      axis.text.x = element_text(margin = margin(5), size =12), 
      legend.text = element_text(size = 12),
      legend.title = element_text(size = 18),
      
      #facet labels
      strip.text.x = element_text(size = 15, face = 'bold', family =font),
      strip.background = element_blank()
    )
  
}
```
Read Data
```{r}
df<-read.csv('data/sub1.csv')
df<- df%>%
  mutate(Experimental.Day = as.factor(Experimental.Day),rtime = as_hms(rtime))
df1 <-df %>%
   mutate(bottle=factor(bottle,levels = c('pre', 'post')),
                        exposure = factor(exposure, levels = c("pre", 'active','post')))%>%
  mutate(ind=factor(ind, levels = c("Loki", "Ragnar", "Haliai", "Caly",'Selkie', "Scylla")))%>%
  filter(Behavior %in% c("left", "right"))%>%
    filter(., grepl("Total",obs)) %>%
  select(ind,Experimental.Day,Subject, Subject_tax,Behavior,exposure,date,rtime,dur, newbehav)
glimpse(df1)


```


Octos: Get side of tank for every 30 seconds
```{r}
interval=30
octos <- df1 %>%
  filter(Subject_tax == "Octopus")%>%
 filter(dur > 30) %>%
  mutate(ntime=as_hms(rtime))

df_new=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())
df_new_octos=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())

for (i in 1:nrow(octos)){
  df_new=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())
  df_new=rbind(df_new, octos[rep(i, round(octos$dur[i]/interval)),])

  for(j in 1:(round(octos$dur[i]/interval))){
  print(c(i,j))
    if(j==1) df_new$ntime[j]=df_new$ntime[j] else df_new$ntime[j]=df_new$ntime[j-1]+as.difftime(interval,units="secs")
  }
  df_new_octos<-rbind(df_new_octos,df_new)
}

#library(lubridate)
df_new_octos$date_time <- as.POSIXct(paste(df_new_octos$date, df_new_octos$ntime),  # Add hours, minutes & seconds
                            format = "%Y-%m-%d %H:%M:%S")
df_new_octos$esttime<-lubridate::round_date(df_new_octos$date_time, unit = '30 seconds')
```

```{r}
interval=30
octos <- df1 %>%
  filter(Subject_tax == "Octopus")%>%
  filter(dur > 30) %>%
  mutate(ntime=as_hms(rtime))

 df_new_octos=octos%>%
   mutate(endtime=ntime+as.difftime(dur,units="secs"))%>%
   mutate(endtime=hms(round(lubridate::seconds_to_period(endtime))))%>%
   mutate(state_start=as.POSIXct(paste(date,ntime),format = "%Y-%m-%d %H:%M:%S"))%>%
   mutate(state_end=as.POSIXct(paste(date,endtime),format = "%Y-%m-%d %H:%M:%S"))%>%
   mutate(states=newbehav) 

```


Clams: Get side of tank for every 30 seconds 
```{r}
interval=30
clams <- df1 %>%
  filter(Subject_tax == "Clam") %>%
  mutate(ntime=as_hms(rtime))

df_new=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())
df_new_clams=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())

for (i in 1:nrow(clams)){
  df_new=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())
  df_new=rbind(df_new, clams[rep(i, round(clams$dur[i]/interval)),])

  for(j in 1:(round(clams$dur[i]/interval))){
  print(c(i,j))
    if(j==1) df_new$ntime[j]=df_new$ntime[j] else df_new$ntime[j]=df_new$ntime[j-1]+as.difftime(interval,units="secs")
  }
  df_new_clams<-rbind(df_new_clams,df_new)
}
#library(lubridate)
df_new_clams$date_time <- as.POSIXct(paste(df_new_clams$date, df_new_clams$ntime),  # Add hours, minutes & seconds
                            format = "%Y-%m-%d %H:%M:%S")
df_new_clams<-df_new_clams %>% mutate(esttime=lubridate::round_date(df_new_clams$date_time, unit = '30 seconds'))%>%
   mutate(events=newbehav)
#write.csv(df_new_clams, "data/lr_clams")
```
Create same side or opposite side as octo predator
```{r}
octo_state=df_new_octos#%>%select(states,state_start,state_end)

clam_state=df_new_clams#%>%select(esttime,events)

library(data.table)
setDT(octo_state, key = c("state_start", "state_end"))
cols <- c("state_start", "state_end")
setDT(clam_state)[, (cols) := esttime]

x=foverlaps(clam_state, octo_state)[, paste0("i.", cols) := NULL]

side_clams=x %>% #select(-contains("i."))%>%
  mutate(octo_side=states,clam_side=events) %>% select(-events,-states)   %>%
  mutate(same = case_when(octo_side == clam_side ~ 1, TRUE ~ 0))
```
Run Bayesian Bernoulli models 
```{r}
library(brms)
library(tidybayes)
side_clams <- side_clams %>%mutate(Block = case_when(ind %in% c("Loki", "Ragnar", "Haliai") ~ 1, TRUE ~ 2))

clam_mod1<- brm(same~exposure,
                data = side_clams,
                family = "bernoulli")
clam_mod1
pp_check(clam_mod1)
plot(clam_mod1)

clam_mod<- brm(same~exposure + (1|ind),
                data = side_clams,
                family = "bernoulli")
clam_mod
pp_check(clam_mod)
plot(clam_mod)

clam_mod2<- brm(same~exposure + (1|Block),
                data = side_clams,
                family = "bernoulli")
clam_mod2
pp_check(clam_mod2)
plot(clam_mod2)
library(loo)

loo<- loo(clam_mod)
waic<-waic(clam_mod)
loo1 <- loo(clam_mod1)
waic1 <- waic(clam_mod1)
loo2 <- loo(clam_mod2)
waic2 <- waic(clam_mod2)
loo_compare(loo, loo1, loo2)
loo_compare(waic, waic1, waic2)
prior_summary(clam_mod)
```

Calculate estimates
```{r}
library(emmeans)
library(tidybayes)
x = emmeans(clam_mod, ~ exposure,
        regrid = "response",epred = TRUE, re_formula = NULL) %>% 
 contrast(method = "revpairwise") %>% as_tibble()

x
emmeans(clam_mod, ~ exposure,
        regrid = "response",epred = TRUE, re_formula = NULL)
clam_x3 = clam_mod %>% emmeans(~exposure, regrid = "response", epred = TRUE, re_formula=NULL) %>% 
  gather_emmeans_draws()
clam_x4 = clam_mod %>% emmeans(~exposure, regrid = "response", epred = TRUE, re_formula=NULL) %>% 
  contrast(method = "revpairwise" ) %>%
  as_tibble()
```
Contrast plot
```{r}
clam_x4=clam_x4 %>% mutate(contrast = factor(contrast, levels = c("post - active",'post - pre', "active - pre")))
clam_xplot <- ggplot(clam_x4, aes(x = contrast, y = estimate,ymin=lower.HPD,ymax=upper.HPD)) +geom_point(size=2, color = "orange")+geom_errorbar(width = .3, color = "orange")+
  theme_thesi()+
  labs(y = "Contrast")+
  #scale_fill_manual(values=c( "#56B4E9", "#CC0000","#33CC33"))+
  theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
        axis.title.y = element_blank(), axis.title.x= element_text(margin = margin(t=5)), plot.title = element_text(hjust = .5))+coord_flip()+geom_hline(yintercept = 0,size=1,linetype="dashed")
clam_xplot
```

Estimate Plot 
```{r}
library(tidybayes)

clam_x3$exposure <- factor(clam_x3$exposure, levels = c("post", "active", 'pre'))

clamp <- ggplot(clam_x3, aes(x = .value, y = exposure, fill = exposure)) +
 stat_halfeye(.width = c(0.8, 0.95), point_interval = "median_hdi",normalize="groups")+
  theme_oct()+
  scale_fill_manual(values=c("#56B4E9", "#CC0000", '#33CC33'))+
 labs( y = "", x = "Probability")+
  theme(legend.position = 'none', axis.title.x = element_text(margin = margin(t = 5))) +
  xlim(0,1)
clamp
ggsave("graphics/PPT/clams_vic.jpg", width = 9.6, height = 4.8, units = "in")

```


Crabs: Get side of tank for every 30 seconds
```{r}
interval=30
crabs <- df1 %>%
  filter(Subject_tax == "Swim Crab") %>%
   filter(dur > 30) %>%
  mutate(ntime=as_hms(rtime))

df_new=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())
df_new_crabs=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())

for (i in 1:nrow(crabs)){
  df_new=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())
  df_new=rbind(df_new, crabs[rep(i, round(crabs$dur[i]/interval)),])

  for(j in 1:(round(crabs$dur[i]/interval))){
  print(c(i,j))
    if(j==1) df_new$ntime[j]=df_new$ntime[j] else df_new$ntime[j]=df_new$ntime[j-1]+as.difftime(interval,units="secs")
  }
  df_new_crabs<-rbind(df_new_crabs,df_new)
}
df_new_crabs$date_time <- as.POSIXct(paste(df_new_crabs$date, df_new_crabs$ntime),  # Add hours, minutes & seconds
                            format = "%Y-%m-%d %H:%M:%S")
df_new_crabs<-df_new_crabs %>% mutate(esttime = round_date(df_new_crabs$date_time, unit = '30 seconds'))%>%
   mutate(events=newbehav)
```
Create same side or opposite side as octo predator
```{r}
octo_state=df_new_octos#%>%select(states,state_start,state_end)

crab_state=df_new_crabs#%>%select(esttime,events)

library(data.table)
setDT(octo_state, key = c("state_start", "state_end"))
cols <- c("state_start", "state_end")
setDT(crab_state)[, (cols) := esttime]

x=foverlaps(crab_state, octo_state)[, paste0("i.", cols) := NULL]

side_crabs=x %>% #select(-contains("i."))%>%
  mutate(octo_side=states,crab_side=events) %>% select(-events,-states)   %>%
  mutate(same = case_when(octo_side == crab_side ~ 1, TRUE ~ 0))
```
Run Bayesian Bernoulli model
```{r}
library(brms)
side_crabs <- side_crabs %>%mutate(Block = case_when(ind %in% c("Loki", "Ragnar", "Haliai") ~ 1, TRUE ~ 2))
crab_mod<- brm(same~exposure,
                data = side_crabs,
                family = "bernoulli")
crab_mod2
pp_check(crab_mod)
plot(crab_mod)
crab_mod1 <- brm(same~exposure + (1|ind),
                data = side_crabs,
                family = "bernoulli")
crab_mod2 <- brm(same~exposure + (1|Block),
                data = side_crabs,
                family = "bernoulli")
loo<- loo(crab_mod)
waic<-waic(crab_mod)
loo1 <- loo(crab_mod1)
waic1 <- waic(crab_mod1)
loo2 <- loo(crab_mod2)
waic2 <- waic(crab_mod2)
loo_compare(loo, loo1, loo2)
loo_compare(waic, waic1, waic2)
```

estimates
```{r}
library(emmeans)
x = emmeans(crab_mod1, ~ exposure,
        regrid = "response") %>% 
 contrast(method = "revpairwise") %>% as_tibble()
x
emmeans(crab_mod1, ~ exposure,
        regrid = "response", epred = TRUE, re_formula=NULL, dpar = 'phi') 
crab_x3 = crab_mod1 %>% emmeans(~exposure, regrid = "response", epred = TRUE, re_formula=NULL) %>% 
  gather_emmeans_draws()
crab_x4 = crab_mod1 %>% emmeans(~exposure, regrid = "response", epred = TRUE, re_formula=NULL) %>% 
  contrast(method = "revpairwise" ) %>%
  as_tibble()
crab_x4
```
Contrast plot
```{r}
crab_x4=crab_x4 %>% mutate(contrast = factor(contrast, levels = c("post - active",'post - pre', "active - pre")))
crab_xplot <- ggplot(crab_x4, aes(x = contrast, y = estimate,ymin=lower.HPD,ymax=upper.HPD)) +geom_point(size=2, color = "orange")+geom_errorbar(width = .3, color = "orange")+
  theme_thesi()+
  #labs(title = "Contrast")+
  #scale_fill_manual(values=c( "#56B4E9", "#CC0000","#33CC33"))+
  theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
        axis.title.y = element_blank(), plot.title = element_text(hjust = .5))+coord_flip()+geom_hline(yintercept = 0,size=1,linetype="dashed")
crab_xplot
```
Estimate Plot
```{r}
crab_x3$exposure <- factor(crab_x3$exposure, levels = c("post", "active", 'pre'))

crabp <- ggplot(crab_x3, aes(x = .value, y = exposure, fill = exposure)) +
 stat_halfeye(.width = c(0.8, 0.95), point_interval = "median_hdi",normalize="groups")+
  theme_oct()+
  scale_fill_manual(values=c("#56B4E9", "#CC0000", '#33CC33'))+
 labs( y = "", x = "Probability")+
  theme(legend.position = 'none',axis.title.x = element_text(margin = margin(t = 5))) +
  xlim(0,1)
crabp

ggsave("graphics/PPT/crabs_vic.jpg", width = 9.6, height = 4.8, units = "in")

```


Hermit Crabs: Get side of tank for every 30 seconds
```{r}
interval=30
hermits <- df1 %>%
  filter(Subject_tax == "Hermit Crab", dur > 30) %>%
  mutate(ntime=as_hms(rtime))

df_new=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())
df_new_hermits=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())

for (i in 1:nrow(hermits)){
  df_new=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())
  df_new=rbind(df_new, hermits[rep(i, round(hermits$dur[i]/interval)),])

  for(j in 1:(round(hermits$dur[i]/interval))){
  print(c(i,j))
    if(j==1) df_new$ntime[j]=df_new$ntime[j] else df_new$ntime[j]=df_new$ntime[j-1]+as.difftime(interval,units="secs")
  }
  df_new_hermits<-rbind(df_new_hermits,df_new)
}
#library(lubridate)
df_new_hermits$date_time <- as.POSIXct(paste(df_new_hermits$date, df_new_hermits$ntime),  # Add hours, minutes & seconds
                            format = "%Y-%m-%d %H:%M:%S")
df_new_hermits<-df_new_hermits %>% mutate(esttime=lubridate::round_date(df_new_hermits$date_time, unit = '30 seconds'))%>%
   mutate(events=newbehav)

```
Create same side or opposite side as octo predator
```{r}
octo_state=df_new_octos#%>%select(states,state_start,state_end)

hermit_state=df_new_hermits#%>%select(esttime,events)

library(data.table)
setDT(octo_state, key = c("state_start", "state_end"))
cols <- c("state_start", "state_end")
setDT(hermit_state)[, (cols) := esttime]

x=foverlaps(hermit_state, octo_state)[, paste0("i.", cols) := NULL]

side_hermits=x %>% select(-contains("i."))%>%
  mutate(octo_side=states,hermit_side=events) %>% select(-events,-states)   %>%
  mutate(same = case_when(octo_side == hermit_side ~ 1, TRUE ~ 0))
```
Run Bayesian Bernoulli model
```{r}
library(brms)
library(tidybayes)
hermit_mod<- brm(same~exposure,
                data = side_hermits,
                family = "bernoulli")
hermit_mod
pp_check(hermit_mod)
plot(hermit_mod)
library(brms)
hermit_mod1<- brm(same~exposure + (1|ind),
                data = side_hermits,
                family = "bernoulli")
hermit_mod1 <- hermit_mod
loo<-loo(hermit_mod)
loo1<-loo(hermit_mod1)
loo_compare(loo,loo1)
```

estimates
```{r}
library(emmeans)
x = emmeans(hermit_mod1, ~ exposure,
        regrid = "response") %>% 
 contrast(method = "revpairwise") %>% as_tibble()

x
emmeans(hermit_mod1, ~ exposure,
        regrid = "response",epred = TRUE, re_formula = NULL)
herm_x3 = hermit_mod1 %>% emmeans(~exposure, regrid = "response", epred = TRUE, re_formula=NULL) %>% 
  gather_emmeans_draws()
herm_x4 = hermit_mod1 %>% emmeans(~exposure, regrid = "response", epred = TRUE, re_formula=NULL) %>% 
  contrast(method = "revpairwise" ) %>%
  as_tibble()
```
Contrast plot
```{r}
herm_x4=herm_x4 %>% mutate(contrast = factor(contrast, levels = c("post - active",'post - pre', "active - pre")))
herm_xplot <- ggplot(herm_x4, aes(x = contrast, y = estimate,ymin=lower.HPD,ymax=upper.HPD)) +geom_point(size=2, color = "orange")+geom_errorbar(width = .3, color = "orange")+
  theme_thesi()+
  #labs(title = "Contrast")+
  #scale_fill_manual(values=c( "#56B4E9", "#CC0000","#33CC33"))+
  theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
        axis.title.y = element_blank(), plot.title = element_text(hjust = .5))+coord_flip()+geom_hline(yintercept = 0,size=1,linetype="dashed")
herm_xplot
```
Estimate Plot
```{r}

herm_x3$exposure <- factor(herm_x3$exposure, levels = c("post", "active", 'pre'))

hermp<- ggplot(herm_x3, aes(x = .value, y = exposure, fill = exposure)) +
 stat_halfeye(.width = c(0.8, 0.95), point_interval = "median_hdi",normalize="groups")+
  theme_oct()+
  scale_fill_manual(values=c("#56B4E9", "#CC0000", '#33CC33'))+
 labs( y = "", x = "Probability")+
  theme(legend.position = 'none',axis.title.x = element_text(margin = margin(t = 5))) +
  xlim(0,1)
hermp
ggsave("graphics/PPT/hermits_vic.jpg", width = 9.6, height = 4.8, units = "in")

```


Snails:Get side of tank for every 30 seconds
```{r}
interval=30
snails <- df1 %>%
  filter(Subject_tax == "Snail", dur > 30) %>%
  mutate(ntime=as_hms(rtime))

df_new=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())
df_new_snails=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())

for (i in 1:nrow(snails)){
  df_new=tibble(ind=factor(),Oleamide.Exposure=factor(),Experimental.Day=factor(),Subject=factor(), Subject_tax = factor(), Behavior=factor(),exposure=factor(),rtime = factor(),date = factor(),dur=numeric(length=0), newbehav = factor(),ntime = hms())
  df_new=rbind(df_new, snails[rep(i, round(snails$dur[i]/interval)),])

  for(j in 1:(round(snails$dur[i]/interval))){
  print(c(i,j))
    if(j==1) df_new$ntime[j]=df_new$ntime[j] else df_new$ntime[j]=df_new$ntime[j-1]+as.difftime(interval,units="secs")
  }
  df_new_snails<-rbind(df_new_snails,df_new)
}
#library(lubridate)
df_new_snails$date_time <- as.POSIXct(paste(df_new_snails$date, df_new_snails$ntime),  # Add hours, minutes & seconds
                            format = "%Y-%m-%d %H:%M:%S")
df_new_snails<-df_new_snails %>% mutate(esttime=lubridate::round_date(df_new_snails$date_time, unit = '30 seconds'))%>%
   mutate(events=newbehav)

```
Create same side or opposite side as octo predator
```{r}
octo_state=df_new_octos#%>%select(states,state_start,state_end)

snail_state=df_new_snails#%>%select(esttime,events)

library(data.table)
setDT(octo_state, key = c("state_start", "state_end"))
cols <- c("state_start", "state_end")
setDT(snail_state)[, (cols) := esttime]

x=foverlaps(snail_state, octo_state)[, paste0("i.", cols) := NULL]

side_snails=x %>% #select(-contains("i."))%>%
  mutate(octo_side=states,snail_side=events) %>% select(-events,-states)   %>%
  mutate(same = case_when(octo_side == snail_side ~ 1, TRUE ~ 0))
```
Run Bayesian Bernoulli model
```{r}
library(brms)
snail_mod<- brm(same~exposure,
                data = side_snails,
                family = "bernoulli")
snail_mod
pp_check(snail_mod)
plot(snail_mod)
snail_mod1 <- brm(same~exposure + (1|ind),
                data = side_snails,
                family = "bernoulli")
snail_mod1
pp_check(snail_mod1)
plot(snail_mod1)
loo<-loo(snail_mod)
loo1<-loo(snail_mod1)
loo_compare(loo,loo1)
```

estimates
```{r}
library(emmeans)
x = emmeans(snail_mod1, ~ exposure,
        regrid = "response") %>% 
 contrast(method = "revpairwise") %>% as_tibble()

x
emmeans(snail_mod1, ~ exposure,
        regrid = "response",epred = TRUE, re_formula=NULL)
snail_x3 = snail_mod1 %>% emmeans(~exposure, regrid = "response", epred = TRUE, re_formula=NULL) %>% 
  gather_emmeans_draws()
snail_x4 = snail_mod1 %>% emmeans(~exposure, regrid = "response", epred = TRUE, re_formula=NULL) %>% 
  contrast(method = "revpairwise" ) %>%
  as_tibble()
```
Contrast plot
```{r}
snail_x4 = snail_x4 %>% mutate(contrast = factor(contrast, levels = c("post - active",'post - pre', "active - pre")))
snail_xplot <- ggplot(snail_x4, aes(x = contrast, y = estimate,ymin=lower.HPD,ymax=upper.HPD)) +geom_point(size=2, color = "orange")+geom_errorbar(width = .3, color = "orange")+
  theme_thesi()+
  #labs(title = "Contrast")+
  #scale_fill_manual(values=c( "#56B4E9", "#CC0000","#33CC33"))+
  theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
        axis.title.y = element_blank(), plot.title = element_text(hjust = .5))+coord_flip()+geom_hline(yintercept = 0,size=1,linetype="dashed")
snail_xplot
```
Estimate Plot
```{r}

snail_x3$exposure <- factor(snail_x3$exposure, levels = c("post", "active", 'pre'))

snailp <- ggplot(snail_x3, aes(x = .value, y = exposure, fill = exposure)) +
 stat_halfeye(.width = c(0.8, 0.95), point_interval = "median_hdi",normalize="groups")+
  theme_oct()+
  scale_fill_manual(values=c("#56B4E9", "#CC0000", '#33CC33'))+
 labs( y = "", x = "Probability")+
  theme(legend.position = 'none',axis.title.x = element_text(margin = margin(t = 5))) +
  xlim(0,1)
snailp
ggsave("graphics/PPT/snails_vic.jpg", width = 9.6, height = 4.8, units = "in")

```


Put all plots together
```{r}
library(patchwork)
hermp + herm_xplot+ crabp + crab_xplot + snailp + snail_xplot+ clamp +clam_xplot+ plot_layout(nrow = 4)
ggsave("graphics/left-right.jpg", width = 6.5, height = 8, units = 'in')
```

Save Workspace 
```{r}
#save.image(file = "Workspaces/Left-Right.RData")
```


