---
title: "Predation2"
author: "Madelyn Hair"
date: "2023-09-08"
output: html_document
---

Some packages
```{r}
library(tidyverse)
library(stringr)
library(hms)
library(glmmTMB)
library(DHARMa)
library(car)
library(bbmle)
library(brms)
library(tidybayes)
library(broom.mixed)

```

Load the workspace here to avoid rerunning the Bayesian models
```{r}
load("GitHub/OctopusPredation/Workspaces/Bayesian Predation_short.RData")
```

**Create your presentation theme_oct()**
```{r}
theme_oct <- function() {
  font <- 'Trebuchet MS' #Same as PPT
  theme_bw() %+replace%
    theme(
      
      #Gridlines
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      panel.border = element_blank(),
      axis.line = element_line(colour = "black"),
       plot.margin = margin(r= 8, t = 8, b = 8, l = 8),
      #Text elements
      plot.title = element_text(family = font, 
                                size = 20,
                                face = 'bold',
                hjust = .5,
                                vjust = 2),
      axis.title = element_text(family = font,
                                size = 15, face = 'bold'), 
      axis.title.x = element_blank(),
     # axis.title.x = element_text(margin = margin(5)),
     axis.title.y = element_text(margin= margin(r=10), angle = 90, size = 18),
    # axis.title.y=element_blank(),
      axis.text = element_text(family = font,
                               size = 15),
     axis.text.y=element_text(size = 12),
      axis.text.x = element_text(margin = margin(5), size =15, face = "bold"), 
      legend.text = element_text(size = 12),
      legend.title = element_text(size = 18),
      
      #facet labels
      strip.text.x = element_text(size = 15, face = 'bold', family =font),
      strip.background = element_blank()
    )
  
}
```
**Create your publication theme_thesi!**
```{r}
theme_thesi <- function() {
  font <- 'Trebuchet MS' #Same as PPT
  theme_bw() %+replace%
    theme(
      
      #Gridlines
      panel.grid.major.x=element_blank(),
      panel.grid.major.y =element_blank(),
      panel.grid.minor.y=element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.border = element_blank(),
      axis.line = element_line(colour = "black"),
      plot.margin = margin(0,0,0,0),
      
      #Text elements
      plot.title = element_text(family = font, 
                                size = 15, face = 'bold',
               hjust = .5, vjust = 2),
      axis.title = element_text(family = font,
                                size = 12, face = 'bold'), 
      axis.title.y = element_text(margin= margin(r=5), angle = 90, size = 12),
      axis.title.x = element_blank(),
      axis.text = element_text(family = font,
                               size = 10),
      axis.text.x = element_text(margin = margin(t = 5), size = 12), 
      axis.text.y = element_text(face = 'bold', margin = margin(r = 5), size = 12),
      legend.text = element_text(size = 12),
      legend.title = element_text(size = 18),
      
      #facet labels
      strip.text.x = element_text(size = 15, face = 'bold', family =font),
      strip.background = element_blank()
    )
  
}
```

Read Data and tidy and truncate to experimental period (12:30-14:00)

```{r}
preds<-read.csv("data/pred.csv") %>%
  mutate(time = as_hms(rtime), Behavior =as.factor(Behavior), exposure = factor(exposure,levels = c("pre", "active", "post")),
         bottle = factor(bottle, levels = c("pre",'post')),
         ind = factor(ind, levels =c("Loki", "Ragnar", "Haliai", "Caly", "Selkie", "Scylla"))
         ) %>%
  filter(Behavior %in% c('Predation','Grope'))

short_preds <- preds %>%
  filter(rtime >= '12:30:30' & rtime <= "14:00:00", Subject == "Octopus",
         Experimental.Day %in%c(2,6,9)) %>%
  mutate(successbin = case_when(Behavior == "Grope" ~ 0, Behavior == 'Predation' & m2 == "Failed" ~ 0, Behavior == "Predation" & m2 == "Successful" ~ 1),
         Experimental.Day = as.factor(Experimental.Day))
```

```{r}
library(brms)
pred_mod <- brm(count ~ exposure , 
                data = psum,
                family = poisson)
pred_mod
plot(pred_mod)
pred_mod1 <- brm(count ~ exposure + (1|Block),
                 data = psum,
                 family = poisson,
                 iter = 50000) 
pred_mod1
plot(pred_mod1)
pp_check(pred_mod1)
pred_mod9<- brm(bf(count~exposure,
                   zi ~ 1), 
                data = psum,
                family = zero_inflated_poisson,
                iter = 50000)
pred_mod9
pp_check(pred_mod9)
pred_mod2<- brm(bf(count~exposure + (1|Block),
                   zi ~ 1), 
                data = psum,
                family = zero_inflated_poisson,
                iter = 50000)
pred_mod2
plot(pred_mod2)
pp_check(pred_mod2)

pred_mod12 <- brm(bf(count~exposure + (1|Block)),
                 data = psum,
                 family = zero_inflated_poisson,
                 iter = 5000)
pred_mod12
plot(pred_mod12)
pp_check(pred_mod12)

pred_mod4 <- brm(bf(count~exposure+Behavior + (1|Block),
                    zi ~ 1),
                 data = psum,
                 family = zero_inflated_poisson,
                 iter=50000, adapt_delta = .9)
pred_mod4
plot(pred_mod4)
pp_check(pred_mod4)

pred_mod5 <- brm(bf(count~exposure*Behavior + (1|Block),
                    zi ~ 1),
                 data = psum,
                 family = zero_inflated_poisson,
                 iter=50000)
pred_mod5
plot(pred_mod5)

pred_mod6 <- brm(bf(count~exposure*Behavior + (1|Block)),
                 data = psum,
                 family = poisson,
                 iter=50000)
pred_mod6
plot(pred_mod6)
pred_mod7 <- brm(bf(count~exposure*Behavior, 
                    zi~1),
                 data = psum,
                 family = zero_inflated_poisson,
                 iter=50000)
pred_mod7

pred_mod8 <- brm(bf(count~exposure*Behavior, 
                    zi~Block),
                 data = psum,
                 family = zero_inflated_poisson,
                 iter=50000)
pred_mod8
pred_mod9<- brm(bf(count~exposure,
                   zi ~ 1), 
                data = psum,
                family = zero_inflated_poisson,
                iter = 50000)
pred_mod10 <- brm(bf(count~exposure,
                    zi ~ Block),
                 data = psum,
                 family = zero_inflated_poisson,
                 iter=50000)
pred_mod3 <- brm(bf(count~exposure + (1|Block),
                    zi~ exposure),
                 data = psum,
                 family = zero_inflated_poisson,
                 iter = 5000)
pred_mod11 <- brm(bf(count~exposure + (1|Block),
                    zi ~ Block),
                 data = psum,
                 family = zero_inflated_poisson,
                 iter=50000)
pred_mod10
plot(pred_mod10)
pp_check(pred_mod10)

prior_summary(pred_mod10)

```

Compare models:
Warning:these model criteria can be very sensitive to complicated models, only trust if other parameters look good.
```{r}
loo1<- loo(pred_mod1)
loo <- loo(pred_mod)
loo2<- loo(pred_mod2)
loo3<- loo(pred_mod3)
loo4<- loo(pred_mod4)
loo5<- loo(pred_mod5)
loo6<- loo(pred_mod6)
loo7<- loo(pred_mod7)
loo8<- loo(pred_mod8)
loo9 <- loo(pred_mod9)
loo10 <- loo(pred_mod10)
loo11<-loo(pred_mod11)
loo12<-loo(pred_mod12)
loo1
loo_compare(loo1, loo, loo2, loo3, loo9, loo10, loo11,loo12)

waic1<- waic(pred_mod1)
waic <- waic(pred_mod)
waic2<- waic(pred_mod2)
waic3<- waic(pred_mod3)
waic4<- waic(pred_mod4)
waic5<- waic(pred_mod5)
waic6<- waic(pred_mod6)
waic7<- waic(pred_mod7)
waic8<- waic(pred_mod8)
waic9 <- waic(pred_mod9)
waic10 <- waic(pred_mod10)
waic11<-waic(pred_mod11)
waic12<-waic(pred_mod12)
loo_compare(waic1, waic, waic2, waic3, waic9, waic10, waic11,waic12)

```
pred_mod10 seems the best fit and most robust

Generate estimates from model
```{r}
library(emmeans)
x3 = pred_mod10 %>% emmeans(~exposure, regrid = "response", epred = TRUE, re_formula=NULL) %>% 
  gather_emmeans_draws()
x4 = pred_mod10 %>% emmeans(~exposure, regrid = "response",epred = TRUE, re_formula=NULL) %>% 
  contrast(method = "revpairwise" ) %>%
  as_tibble()

```

Create contrast plot of predation/grope events
```{r}
x4=x4 %>% mutate(contrast = factor(contrast, levels = c("post - active",'post - pre', "active - pre")))
xplot <- ggplot(x4, aes(x = contrast, y = estimate,ymin=lower.HPD,ymax=upper.HPD)) +geom_point(size=2, color = "orange")+geom_errorbar(width = .3, color = "orange")+
  theme_oct()+
  labs(y = "Contrast")+
  #scale_fill_manual(values=c( "#56B4E9", "#CC0000","#33CC33"))+
  theme(axis.text.x = element_text(size = 12),axis.text.y = element_text(size = 12, face="bold"),
        axis.title.y = element_blank(), axis.title.x = element_text(margin = margin(t=5)),plot.title = element_text(hjust = .5))+coord_flip()+geom_hline(yintercept = 0,size=1,linetype="dashed")
xplot
```

Create half-eye plot of Predation/Grope events
```{r}
x3$exposure <- factor(x3$exposure, levels = c("post", "active", 'pre'))
font <- 'Trebuchet MS'
predp<-ggplot(x3, aes(x = .value, y = exposure, fill = exposure)) +
 stat_halfeye(.width = c(0.8, 0.95), point_interval = "median_hdi", normalize="groups")+
  theme_oct()+
  scale_fill_manual(values=c("#56B4E9", "#CC0000", '#33CC33'))+
 labs( y = "", x = "Log of Events")+
  theme(legend.position = 'none', axis.title.x = element_text(margin = margin(t = 5)), axis.text.y=element_text(margin=margin(r=5), face = "bold", size = 15), 
        axis.text.x=element_text(size = 12, face = NULL)) +
  xlim(0,3)
predp

```

Patch figures together
```{r}
library(patchwork)
predp + xplot + plot_annotation(title = "Trophic Interactions", theme = theme(plot.title = element_text(size = 16, face = 'bold', family = font)))

```

